The impact of environmental shocks on children's schooling in Bolivia

### 2020-05-07 paper_draft.Rmd
trying to get lagged data in

export_summary_table(dfSummary(flood_summary))
```
The drought data also spans the years 2005-2012 and shows the frequency of droughts in each municipality by year.

>>>>

#lagged flood data created in excel
library(xlsx)
write.xlsx(flood_summary, "C:\Users\katya\Documents\MyDocuments\A Smith College Spring Semester\Natural Resource Economics\seminar-paper-katyagi21/lagflood.xlsx")
#library(DataCombine)
#flood_lags <- slide(flood_summary, Var = "floods", slideBy = -1)

export_summary_table(dfSummary(flood_summary))

```
The drought data also spans the years 2005-2012 and shows the frequency of droughts in each municipality by year.
